### 2013-03-28 au_topology_seminar_talk_2013_02_18.tex
Updated TODOs and fixed seminar talk

We construct a ZFC example given by Gary Gruenhage, inpsired by a ZFC+$\lnot$SH example due to Stephen Watson \cite{Watson}. We require a slight modification of a result of Gruenhage and Michael \cite{Michael}:

\begin{theorem}\label{michael}
Let $X$ be a meta-Lindel\"of, locally Lindel\"of regular space, and let $\mc{B}$ be a base of cardinality $\kappa$ for $X$. Then $X$ has a cover $\mc{B}'\subseteq\mc{B}$ of cardinality $\kappa$ such that $\{\close{B}:B\in\mc{B}'\}$ is point-countable.
\end{theorem}

\begin{proof}
asdf?
\end{proof}

\begin{theorem}\label{basic_x}
There exists a compact, zero-dimensional topological space $X$ which has a point-countable cover $\mc{U} = \{U_c : c \in 2^\omega\}$ of clopen sets which is not $\sigma$-point-finite (the union of countably-many point-finite collections).
\end{theorem}

@@

Let $\mc{B}$ be a clopen base for $X$ of cardinality $\leq 2^\omega$ which is a refinement of $\mc{V}$.  Then as $X$ is metaLindel\"of, locally Lindel\"of, and regular, by Thm \ref{michael}, let $\mc{U}\subseteq \mc{B}$ be a point-countable clopen refinement of $\mc{V}$ of cardinality $2^\omega$, which cannot be $\sigma$-point-finite.

% TODO finish this for \leq 2^\omega
\end{proof}

\begin{definition}
Using the $X$ from Theorem \ref{basic_x}, let \[\mathbb{X} = (X \times 2^{<\omega}) \cup 2^\omega\] compose a topological sum of $2^{<\omega}$ copies of $X$ along with a discrete copy of the Cantor Set $\leq 2^\omega$, and add open (in fact, compact) neighborhoods of the form: 
  \[
    B_c = c \cup (U_c \times \{c\rest n : n < \omega\})
  \]
as seen in Figure \ref{fig:cantor_tree}.
\end{definition}

@@

\begin{definition}
Let $S\in[2^\omega]^{<\omega}$ and $m<\omega$. Define 
  \[
    K_S = \bigcup_{c \in S} B_c
  \] 
  \[ 
    A = \{z^\frown \<1\> : z \in 1^{<\omega}\}
  \] 
  \[ 
    K^*_S = K_S \setminus (X \times A)
  \] 
  \[
    L_m = X \times 2^{<m}
  \] 
and observe that every compact set is dominated by the compact set $K^*_S \cup L_m$ for some $S,m$.

@@

\begin{proof}
This is actually a corollary of Gruenhage's theorem in \cite{G2}: $\mathbb{X}$ is locally compact (each point is either in some $X$ or in some $B_c$) but not metacompact (any cover of $2^\omega$ necessarily will have infinite overlap at some $X \times \{s\}$). However, we proceed with a direct game-theoretic proof.

@@

There exists some $f: 2^\omega \to \omega$ such that for all $x\in U_c$, $\sigma'(x,f(c))$ covers some $B_c \setminus L_m$. (If not, $P$ counters by simply always playing in $B_c \setminus L_m$.)

@@

\begin{proof}
Suppose $\sigma(\<x,s\>,\<y,t\>)$ was a winning 2-tactical strategy. Without loss of generality we assume it ignores order. We may define $S(x,y,n)\in [2^\omega]^{<\omega}$ (increasing on $n$) and $n<m(x,y,n)<\omega$ such that for each $(x,y)$,
  \[
    \bigcup_{s,t \in 2^{\leq n}} \sigma(\<x,s\>,\<y,t\>) \subseteq 
    K^*_{S(x,y,n)} \cup L_{m(x,y,n)}
  \]
and so we assume
  \[
    \sigma(\<x,s\>,\<y,t\>) =
    K^*_{S(x,y,\max(|s|,|t|))} \cup L_{m(x,y,\max(|s|,|t|))}
  \]

@@

Suppose
\[
\<x_0, s_0\>, \<x_1, s_1\>, \<x_2, s_2\>, \dots
\]
successfully countered $\tau$ by clustering at $c\in 2^\omega$ (the strategy trivially prevents clustering elsewhere). Let $z_n = \<0,\dots,0\>$ with $n$ zeros. We claim
\[
\<x_0, s_0\>, \<x', {z_{m(x_0,x',|s_0|)}}^\frown\<1\>\>, \<x_1, s_1\>, \<x', {z_{m(x_1,x',|s_1|)}}^\frown\<1\>\>,  \<x_2, s_2\>, \<x', {z_{m(x_2,x',|s_2|)}}^\frown\<1\>\>, \dots
\]
is a successful counter to $\sigma$.

@@

Suppose $\sigma(\<x_0,s_0\>,\dots,\<x_{k},s_{k}\>)$ was a winning $(k+1)$-tactical strategy. Without loss of generality we assume it ignores order. We may define $S(x_0,\dots,x_{k},n)\in [2^\omega]^{<\omega}$ (increasing on $n$) and $n<m(x_0,\dots,x_{k},n)<\omega$ such that for each $(x_0,\dots,x_{k})$,
  \[
    \bigcup_{s_0,\dots,s_k \in 2^{\leq n}} \sigma(\<x_0,s_0\>,\dots,\<x_{k},s_{k}\>) \subseteq 
    K^*_{S(x_0,\dots,x_{k},n)} \cup L_{m(x_0,\dots,x_{k},n)}
  \]
and so we assume
  \[
    \sigma(\<x_0,s_0\>,\dots,\<x_{k},s_{k}\>) =
    K^*_{S(x_0,\dots,x_{k},\max(|s_0|,\dots,|s_k|))} \cup L_{m(x_0,\dots,x_{k},\max(|s_0|,\dots,|s_k|))}
  \]

@@

Suppose
\[
\<x_0, s_0\>, \<x_1, s_1\>, \<x_2, s_2\>, \dots
\]
successfully countered $\tau$ by clustering at $c\in 2^\omega$ (the strategy trivially prevents clustering elsewhere). Let $z_n = \<0,\dots,0\>$ with $n$ zeros. We claim
\[
  \<x_0, s_0\>, 
  \<x', {z_{M^0(x_0,|s_0|)}}^\frown\<1\>\>,
  \<x', {z_{M^1(x_0,|s_0|)}}^\frown\<1\>\>, 
  \dots, 
  \<x', {z_{M^{k-1}(x_0,|s_0|)}}^\frown\<1\>\>,
\]
\[
  \<x_1, s_1\>, 
  \<x', {z_{M^0(x_1,|s_1|)}}^\frown\<1\>\>, 
  \<x', {z_{M^1(x_1,|s_1|)}}^\frown\<1\>\>, 
  \dots, 
  \<x', {z_{M^{k-1}(x_1,|s_1|)}}^\frown\<1\>\>, 
  \dots
\]
is a successful counter to $\sigma$.

>>>>

We construct a ZFC example given by Gary Gruenhage, inpsired by a ZFC+$\lnot$SH example due to Stephen Watson \cite{Watson}. We require a result of Gruenhage and Michael \cite{Michael}:

\begin{theorem}\label{michael}
Let $X$ be a meta-Lindel\"of, locally Lindel\"of regular space, and let $\mc{B}$ be a base for $X$. Then $X$ has a cover $\mc{B}'\subseteq\mc{B}$ such that $\{\close{B}:B\in\mc{B}'\}$ is point-countable.
\end{theorem}

\begin{theorem}\label{basic_x}
There exists a compact, zero-dimensional topological space $X$ and an uncountable subspace $C\subseteq 2^\omega$ of the Cantor Set, such that $X$ has a point-countable cover $\mc{U} = \{U_c : c \in C\}$ of clopen sets which is not $\sigma$-point-finite (the union of countably-many point-finite collections).
\end{theorem}

@@

Let $\mc{B}$ be a clopen base for $X$ of cardinality $2^\omega$ which is a refinement of $\mc{V}$.  Then as $X$ is metaLindel\"of, locally Lindel\"of, and regular, by Thm \ref{michael}, let $\mc{U}\subseteq \mc{B}$ be a point-countable clopen refinement of $\mc{V}$ of cardinality $\leq 2^\omega$, which cannot be $\sigma$-point-finite (and is thus uncountable).
\end{proof}

\begin{definition}
Using the $X$ from Theorem \ref{basic_x}, let \[\mathbb{X} = (X \times 2^{<\omega}) \cup 2^\omega\] compose a topological sum of $2^{<\omega}$ copies of $X$ along with a discrete copy of a subspace $C \subseteq 2^\omega$ of the Cantor Set, and add open (in fact, compact) neighborhoods of the form: 
  \[
    B_c = c \cup (U_c \times \{c\rest n : n < \omega\})
  \]
as seen in Figure \ref{fig:cantor_tree}.
\end{definition}

@@

\begin{definition}
Let $S\in[C]^{<\omega}$ and $m<\omega$. Define 
  \[
    K_S = \bigcup_{c \in S} B_c
  \] 
  \[ 
    A = \{z^\frown \<1\> : z \in 1^{<\omega}\}
  \] 
  \[ 
    K^*_S = K_S \setminus (X \times A)
  \] 
  \[
    L_m = X \times 2^{<m}
  \] 
and observe that every compact set is dominated by the compact set $K^*_S \cup L_m$ for some $S,m$.

@@

\begin{proof}
This is actually a corollary of Gruenhage's theorem in \cite{G2}: $\mathbb{X}$ is locally compact (each point is either in some $X$ or in some $B_c$) but not metacompact (any cover of $C$ necessarily will have infinite overlap at some $X \times \{s\}$). However, we proceed with a direct game-theoretic proof.

@@

There exists some $f: C \to \omega$ such that for all $x\in U_c$, $\sigma'(x,f(c))$ covers some $B_c \setminus L_m$. (If not, $P$ counters by simply always playing in $B_c \setminus L_m$.)

@@

\begin{proof}
Suppose $\sigma(\<x,s\>,\<y,t\>)$ was a winning 2-tactical strategy. Without loss of generality we assume it ignores order. We may define $S(x,y,n)\in [C]^{<\omega}$ (increasing on $n$) and $n<m(x,y,n)<\omega$ such that for each $(x,y)$,
  \[
    \bigcup_{s,t \in 2^{\leq n}} \sigma(\<x,s\>,\<y,t\>) \subseteq 
    K^*_{S(x,y,n)} \cup L_{m(x,y,n)}
  \]
and so we assume
  \[
    \sigma(\<x,s\>,\<y,t\>) =
    K^*_{S(x,y,\max(|s|,|t|))} \cup L_{m(x,y,\max(|s|,|t|))}
  \]

@@

Suppose
\[
\<x_0, s_0\>, \<x_1, s_1\>, \<x_2, s_2\>, \dots
\]
successfully countered $\tau$ by clustering at $c\in C$ (the strategy trivially prevents clustering elsewhere). Let $z_n = \<0,\dots,0\>$ with $n$ zeros. We claim
\[
\<x_0, s_0\>, \<x', {z_{m(x_0,x',|s_0|)}}^\frown\<1\>\>, \<x_1, s_1\>, \<x', {z_{m(x_1,x',|s_1|)}}^\frown\<1\>\>,  \<x_2, s_2\>, \<x', {z_{m(x_2,x',|s_2|)}}^\frown\<1\>\>, \dots
\]
is a successful counter to $\sigma$.

@@

Suppose $\sigma(\<x_0,s_0\>,\dots,\<x_{k},s_{k}\>)$ was a winning $(k+1)$-tactical strategy. Without loss of generality we assume it ignores order. We may define $S(x_0,\dots,x_{k},n)\in [C]^{<\omega}$ (increasing on $n$) and $n<m(x_0,\dots,x_{k},n)<\omega$ such that for each $(x_0,\dots,x_{k})$,
  \[
    \bigcup_{s_0,\dots,s_k \in 2^{\leq n}} \sigma(\<x_0,s_0\>,\dots,\<x_{k},s_{k}\>) \subseteq 
    K^*_{S(x_0,\dots,x_{k},n)} \cup L_{m(x_0,\dots,x_{k},n)}
  \]
and so we assume
  \[
    \sigma(\<x_0,s_0\>,\dots,\<x_{k},s_{k}\>) =
    K^*_{S(x_0,\dots,x_{k},\max(|s_0|,\dots,|s_k|))} \cup L_{m(x_0,\dots,x_{k},\max(|s_0|,\dots,|s_k|))}
  \]

@@

Suppose
\[
\<x_0, s_0\>, \<x_1, s_1\>, \<x_2, s_2\>, \dots
\]
successfully countered $\tau$ by clustering at $c\in C$ (the strategy trivially prevents clustering elsewhere). Let $z_n = \<0,\dots,0\>$ with $n$ zeros. We claim
\[
  \<x_0, s_0\>, 
  \<x', {z_{M^0(x_0,|s_0|)}}^\frown\<1\>\>,
  \<x', {z_{M^1(x_0,|s_0|)}}^\frown\<1\>\>, 
  \dots, 
  \<x', {z_{M^{k-1}(x_0,|s_0|)}}^\frown\<1\>\>,
\]
\[
  \<x_1, s_1\>, 
  \<x', {z_{M^0(x_1,|s_1|)}}^\frown\<1\>\>, 
  \<x', {z_{M^1(x_1,|s_1|)}}^\frown\<1\>\>, 
  \dots, 
  \<x', {z_{M^{k-1}(x_1,|s_1|)}}^\frown\<1\>\>, 
  \dots
\]
is a successful counter to $\sigma$.
